Performance Evaluation of Big Data Processing Strategies for Neuroimaging

### 2018-12-13 paper.tex
Added @shots47s

\author{
  \IEEEauthorblockN{
    Val\'erie Hayot-Sasson and 
    Tristan Glatard
  }\\
  \IEEEauthorblockA{
    Department of Computer Science and Software Engineering, Concordia University, Montreal, Qu\'ebec, Canada
  }
}

>>>>

\author{
  \IEEEauthorblockN{
    Val\'erie Hayot-Sasson$^1$, Shawn T Brown$^2$ and 
    Tristan Glatard$^1$
  }\\
  \IEEEauthorblockA{
    $^1$Department of Computer Science and Software Engineering, Concordia University, Montreal, Canada\\
    $^2$Montreal Neurological Institute, McGill University, Montreal, Canada
  }
}
